Designing for Multiple Use and At-Risk Users: Tor Configuration Launcher

### 2016-03-29 pets2017-paper/pets2017-paper.tex
edit methodology sections.

\section{Qualitative Analysis of the Existing Interface (Study 1)}
\subsection{Motivation} 
\subsection{Methodology} 
\subsubsection{Simulated censorship environments}
We simulated three censorship environments for our experiment.
These reproducible, stable environments are informed by our experience 
with pluggable transports and knowledge of commonly seen censorship 
techniques. Their goal in our user study is not to replicate the network 
environment in any particular country, but to require our participants to 
configure Tor Browser in distinct configurations.

@@

@@

\section{Quantitative Analysis of the Interfaces (Study 2)}

@@

\subsection{Methodology} 
{\color {red} 
What to talk about in this section: 
\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt 
\item experiment design
\item how we chose our metrics
\item how we collected our metrics
\end{itemize} 
}

>>>>

\section{Qualitative Analysis of the Existing Interface (Study 1)}
\subsection{Motivation} 
\subsection{Methodology} 
\subsubsection{Setup}
\label{sec:setup}
We simulated three censorship environments for our experiment.
These reproducible, stable environments are informed by our experience 
with pluggable transports and knowledge of commonly seen censorship 
techniques. Their goal in our user study is not to replicate the network 
environment in any particular country, but to require our participants to 
configure Tor Browser in distinct configurations.

@@

\subsubsection{Recruitment}

@@

\section{Quantitative Analyses of the Interfaces (Study 2)}

@@

\subsection{Methodology} 
\subsubsection{Setup}
For consistency, we simulated the same three censorship environments from 
our qualitative user study. Details of the mild, intermediate, and advanced 
censorship environments and what configurations are necessary for a 
successful connection can be found in Section \ref{sec:setup}.

\subsubsection{Recruitment}
\subsubsection{Procedure}
\subsubsection{Results}
